### 2020-04-29 README.Rmd
Builtup area buffers

```{r, include = FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  echo = FALSE,
  collapse = TRUE,
  comment = "#>"
)
library(tidyverse)
library(sf)
library(tmap)
tmap_mode("view")
# piggyback::pb_download("las_top.Rds")
pct_las = sf::read_sf("https://github.com/cyipt/tempCycleways/releases/download/0.1/pct_la_summaries.geojson")
las_top = readRDS("las_top.Rds")
rsf = readRDS("rsf_grouped_long.Rds")
```

@@

```{r}
roads = rsf %>% filter(region == "London", pctgov > 500)
tm_shape(roads) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_view(set.view = 11) + tm_scale_bar()
```

@@

```{r}
roads = rsf %>% filter(region == "Birmingham", pctgov > 100)
tm_shape(roads) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_view(set.view = 12) + tm_scale_bar()
```

@@

```{r}
roads = rsf %>% filter(region == "Manchester", pctgov > 100)
region_centre = tmaptools::geocode_OSM("Manchester", as.sf = TRUE)
region_buff = stplanr::geo_buffer(region_centre, dist = 7000)
roads = st_intersection(roads, region_buff)
tm_shape(roads) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_view(set.view = 12) + tm_scale_bar()
```

@@

```{r}
roads = rsf %>% filter(region == "Leeds", pctgov > 100)
region_centre = tmaptools::geocode_OSM("Leeds", as.sf = TRUE)
region_buff = stplanr::geo_buffer(region_centre, dist = 3000)
roads = st_intersection(roads, region_buff)
tm_shape(roads) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_scale_bar()
```

@@

```{r}
roads = rsf %>% filter(region == "Liverpool", pctgov > 100)
region_centre = tmaptools::geocode_OSM("Liverpool", as.sf = TRUE)
region_buff = stplanr::geo_buffer(region_centre, dist = 9000)
roads = st_intersection(roads, region_buff)
tm_shape(roads) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_view(set.view = 12) + tm_scale_bar()
```

@@

```{r}
region = pct_las %>% filter(name == "Bristol")
region = sf::st_make_valid(region)
roads = rsf %>% filter(region == "Bristol", pctgov > 100)
roads = roads[region, ]
roads = st_intersection(roads, region)
tm_shape(roads) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_shape(region) + tm_borders() +
  tm_scale_bar() 
```

@@

```{r}
roads = rsf %>% filter(region == "Leicester", pctgov > 100)
region_centre = tmaptools::geocode_OSM("Leicester", as.sf = TRUE)
region_buff = stplanr::geo_buffer(region_centre, dist = 9000)
roads = st_intersection(roads, region_buff)
tm_shape(roads) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_view(set.view = 12) + tm_scale_bar()
```

@@

```{r}
roads = rsf %>% filter(region == "Sheffield", pctgov > 100)
region_centre = tmaptools::geocode_OSM("Sheffield", as.sf = TRUE)
region_buff = stplanr::geo_buffer(region_centre, dist = 9000)
roads = st_intersection(roads, region_buff)
tm_shape(roads) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_view(set.view = 12) + tm_scale_bar()
```

@@

```{r}
roads = rsf %>% filter(region == "Newcastle", pctgov > 100)
region_centre = tmaptools::geocode_OSM("Newcastle", as.sf = TRUE)
region_buff = stplanr::geo_buffer(region_centre, dist = 9000)
roads = st_intersection(roads, region_buff)
tm_shape(roads) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_view(set.view = 12) + tm_scale_bar()
```

@@

```{r}
roads = rsf %>% filter(region == "Cambridge", pctgov > 400)
tm_shape(roads) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_view(set.view = 13) + tm_scale_bar()
```

>>>>

```{r, include = FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  echo = FALSE,
  collapse = TRUE,
  comment = "#>"
)
library(tidyverse)
library(sf)
library(tmap)
tmap_mode("view")
piggyback::pb_download("las_top.Rds")
pct_las = sf::read_sf("https://github.com/cyipt/tempCycleways/releases/download/0.1/pct_la_summaries.geojson")
las_top = readRDS("las_top.Rds")
st_make_valid(las_top)
piggyback::pb_download("rsf_grouped_long.Rds")
rsf = readRDS("rsf_grouped_long.Rds")
piggyback::pb_download("Builtup_Areas_December_2011_Boundaries_V2.geojson")
builtup = sf::read_sf("Builtup_Areas_December_2011_Boundaries_V2.geojson") %>% sf::st_transform(27700)
```

@@

```{r}
##Mask not required for London, so no need to slow down the code unnecessarily
# london_centroids = get_pct_centroids("london",geography = "lsoa") %>% sf::st_transform(27700)
# london_lsoa_buff = st_buffer(x = london_centroids, dist = 1000)
# london_res_buff = st_intersection(builtup,london_lsoa_buff) %>% st_union()
roads = rsf %>% filter(region == "London", pctgov > 500)
# roads = roads %>% st_transform(27700) %>% st_intersection(london_res_buff) %>% st_transform(4326)
tm_shape(roads) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_view(set.view = 11) + tm_scale_bar()
```

@@

```{r}
birmingham_centroids = get_pct_centroids("west-midlands",geography = "lsoa") %>% sf::st_transform(27700)
birmingham_lsoa_buff = st_buffer(x = birmingham_centroids, dist = 1000)
birmingham_res_buff = st_intersection(builtup,birmingham_lsoa_buff) %>% st_union()
roads = rsf %>% filter(region == "Birmingham", pctgov > 100)
roads = roads %>% st_transform(27700) %>% st_intersection(birmingham_res_buff) %>% st_transform(4326)
tm_shape(roads) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_view(set.view = 12) + tm_scale_bar()
```

@@

```{r}
manchester_centroids = get_pct_centroids("greater-manchester",geography = "lsoa") %>% sf::st_transform(27700)
manchester_lsoa_buff = st_buffer(x = manchester_centroids, dist = 1000)
manchester_res_buff = st_intersection(builtup,manchester_lsoa_buff) %>% st_union()
roads = rsf %>% filter(region == "Manchester", pctgov > 100)
roads = roads %>% st_transform(27700) %>% st_intersection(manchester_res_buff) %>% st_transform(4326)
region_centre = tmaptools::geocode_OSM("Manchester", as.sf = TRUE)
region_buff = stplanr::geo_buffer(region_centre, dist = 7000)
roads = st_intersection(roads, region_buff)
tm_shape(roads) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_view(set.view = 12) + tm_scale_bar()
```

@@

```{r}
leeds_centroids = get_pct_centroids("west-yorkshire",geography = "lsoa") %>% sf::st_transform(27700)
leeds_lsoa_buff = st_buffer(x = leeds_centroids$geometry, dist = 1000)
leeds_res_buff = st_intersection(builtup,leeds_lsoa_buff) %>% st_union()
roads = rsf %>% filter(region == "Leeds", pctgov > 100)
roads = roads %>% st_transform(27700) %>% st_intersection(leeds_res_buff) %>% st_transform(4326)
region_centre = tmaptools::geocode_OSM("Leeds", as.sf = TRUE)
region_buff = stplanr::geo_buffer(region_centre, dist = 3000)
roads = st_intersection(roads, region_buff)
tm_shape(roads) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_scale_bar()
```

@@

```{r}
liverpool_centroids = get_pct_centroids("liverpool-city-region",geography = "lsoa") %>% sf::st_transform(27700)
liverpool_lsoa_buff = st_buffer(x = liverpool_centroids, dist = 1000)
liverpool_res_buff = st_intersection(builtup,liverpool_lsoa_buff) %>% st_union()
roads = rsf %>% filter(region == "Liverpool", pctgov > 100)
region_centre = tmaptools::geocode_OSM("Liverpool", as.sf = TRUE)
region_buff = stplanr::geo_buffer(region_centre, dist = 9000)
roads = st_intersection(roads, region_buff)
roads = roads %>% st_transform(27700) %>% st_intersection(liverpool_res_buff) %>% st_transform(4326)
tm_shape(roads) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_view(set.view = 12) + tm_scale_bar()
```

@@

```{r}
bristol_centroids = get_pct_centroids("avon",geography = "lsoa") %>% sf::st_transform(27700)
bristol_lsoa_buff = st_buffer(x = bristol_centroids, dist = 1000)
bristol_res_buff = st_intersection(builtup,bristol_lsoa_buff) %>% st_union()
region = pct_las %>% filter(name == "Bristol")
region = sf::st_make_valid(region)
roads = rsf %>% filter(region == "Bristol", pctgov > 100)
roads = roads[region, ]
roads = st_intersection(roads, region)
roads = roads %>% st_transform(27700) %>% st_intersection(bristol_res_buff) %>% st_transform(4326)
tm_shape(roads) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_shape(region) + tm_borders() +
  tm_scale_bar() 
```

@@

```{r}
leicester_centroids = get_pct_centroids("leicestershire",geography = "lsoa") %>% sf::st_transform(27700)
leicester_lsoa_buff = st_buffer(x = leicester_centroids, dist = 1000)
leicester_res_buff = st_intersection(builtup,leicester_lsoa_buff) %>% st_union()
roads = rsf %>% filter(region == "Leicester", pctgov > 100)
region_centre = tmaptools::geocode_OSM("Leicester", as.sf = TRUE)
region_buff = stplanr::geo_buffer(region_centre, dist = 9000)
roads = st_intersection(roads, region_buff)
roads = roads %>% st_transform(27700) %>% st_intersection(leicester_res_buff) %>% st_transform(4326)
tm_shape(roads) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_view(set.view = 12) + tm_scale_bar()
```

@@

```{r}
sheffield_centroids = get_pct_centroids("south-yorkshire",geography = "lsoa") %>% sf::st_transform(27700)
sheffield_lsoa_buff = st_buffer(x = sheffield_centroids, dist = 1000)
sheffield_res_buff = st_intersection(builtup,sheffield_lsoa_buff) %>% st_union()
roads = rsf %>% filter(region == "Sheffield", pctgov > 100)
region_centre = tmaptools::geocode_OSM("Sheffield", as.sf = TRUE)
region_buff = stplanr::geo_buffer(region_centre, dist = 9000)
roads = st_intersection(roads, region_buff)
roads = roads %>% st_transform(27700) %>% st_intersection(sheffield_res_buff) %>% st_transform(4326)
tm_shape(roads) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_view(set.view = 12) + tm_scale_bar()
```

@@

```{r}
newcastle_centroids = get_pct_centroids("north-east",geography = "lsoa") %>% sf::st_transform(27700)
newcastle_lsoa_buff = st_buffer(x = newcastle_centroids, dist = 1000)
newcastle_res_buff = st_intersection(builtup,newcastle_lsoa_buff) %>% st_union()
roads = rsf %>% filter(region == "Newcastle", pctgov > 100)
region_centre = tmaptools::geocode_OSM("Newcastle", as.sf = TRUE)
region_buff = stplanr::geo_buffer(region_centre, dist = 9000)
roads = st_intersection(roads, region_buff)
roads = roads %>% st_transform(27700) %>% st_intersection(newcastle_res_buff) %>% st_transform(4326)
tm_shape(roads) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_view(set.view = 12) + tm_scale_bar()
```

@@

```{r}
cambridge_centroids = get_pct_centroids("cambridgeshire",geography = "lsoa") %>% sf::st_transform(27700)
cambridge_lsoa_buff = st_buffer(x = cambridge_centroids, dist = 1000)
cambridge_res_buff = st_intersection(builtup,cambridge_lsoa_buff) %>% st_union()
roads = rsf %>% filter(region == "Cambridge", pctgov > 400)
roads = roads %>% st_transform(27700) %>% st_intersection(cambridge_res_buff) %>% st_transform(4326)
tm_shape(roads) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_view(set.view = 13) + tm_scale_bar()
```
